Analyzing changes in Canadian grocery prices

### 2024-11-14 paper/paper.qmd

```{r}
#| label: fig1
#| fig-cap: Each boxplot shows the distribution of numeric reliability grades for the top 5 pollsters, with individual poll grades represented by jittered points.
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig2
#| fig-cap: Each boxplot shows the distribution of numeric reliability grades for the top 5 pollsters, with individual poll grades represented by jittered points.
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig3
#| fig-cap: Each boxplot shows the distribution of numeric reliability grades for the top 5 pollsters, with individual poll grades represented by jittered points.
#| echo: false
#| warning: false
#| message: false

@@

```
Figure 3: Relationship Between Previous and Current Prices. This scatter plot with a linear regression line shows the correlation between previous and current prices. A positive relationship would indicate that higher previous prices predict higher current prices, implying potential price stability or gradual price changes in the grocery market.

@@

```{r}
#| label: fig4
#| fig-cap: Each boxplot shows the distribution of numeric reliability grades for the top 5 pollsters, with individual poll grades represented by jittered points.
#| echo: false
#| warning: false
#| message: false

@@

Figure 4: Distribution of Price Differences (Filtered). This histogram illustrates the frequency of price changes across products, with extreme values beyond three standard deviations removed for clarity. The concentration around zero suggests that small price adjustments are most common, while the presence of both negative and positive values indicates instances of both price increases and decreases. This distribution provides insight into the stability and variability of pricing across vendors.
## Model Evaluation

@@

>>>>

```{r}
#| label: fig-avg-curr-price
#| fig-cap: Average Current Price by Vendor. This bar plot shows the average price of products sold by each grocery vendor in Canadian dollars (CAD). Variations in pricing suggest differences in market positioning or pricing strategies among vendors, with some retailers consistently offering higher or lower prices across product categories.
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-avg-price-diff
#| fig-cap: Average Price Difference by Vendor. This bar plot shows the average price change per vendor, highlighting retailers with the most significant pricing adjustments. Positive differences suggest recent price increases, while negative differences indicate reductions, reflecting possible discounting or competitive pricing strategies.
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-past-curr
#| fig-cap: Relationship Between Previous and Current Prices. This scatter plot with a linear regression line shows the correlation between previous and current prices. A positive relationship would indicate that higher previous prices predict higher current prices, implying potential price stability or gradual price changes in the grocery market.
#| echo: false
#| warning: false
#| message: false

@@

@@

```{r}
#| label: fig-dist-price
#| fig-cap: Relationship Between Previous and Current Prices. This scatter plot with a linear regression line shows the correlation between previous and current prices. A positive relationship would indicate that higher previous prices predict higher current prices, implying potential price stability or gradual price changes in the grocery market.
#| echo: false
#| warning: false
#| message: false

@@

<!-- Figure 4: Distribution of Price Differences (Filtered). This histogram illustrates the frequency of price changes across products, with extreme values beyond three standard deviations removed for clarity. The concentration around zero suggests that small price adjustments are most common, while the presence of both negative and positive values indicates instances of both price increases and decreases. This distribution provides insight into the stability and variability of pricing across vendors. -->

## Model Evaluation

@@

=======
>>>>>>> 3b05c34e7a7a3720d0e488dcd31eaaaa4c292cae
